Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques

### 2018-02-05 paper/gloaguenNmfTraffic.tex
distanceCosLinDisplay improved

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/bloc_diagram_NMF_EN.pdf}
    \caption{Block diagram of the NMF experience with the dictionary design composed from a second sound database}
    \label{fig:bloc_nmf}
\end{figure}

@@

\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}C{2cm}@{}}
	\hline
    \textbf{\begin{tabular}[c]{@{}l@{}}experimental \\ factors\end{tabular}} & modalities & \begin{tabular}[c]{@{}l@{}}number  \\ of level\end{tabular}\\ \toprule
\end{tabularx}

@@

\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}@{}C{2cm}}
	\hline
    \textbf{\begin{tabular}[c]{@{}l@{}}experimental \\ factors\end{tabular}} & modalities & \begin{tabular}[c]{@{}l@{}}number \\ of modality\end{tabular}\\ \toprule
\end{tabularx}

@@

\begin{figure}[t!]
    \centering
    \begin{subfigure}[t]{0.47\linewidth}
        \centering
       \includegraphics[height=4.5cm]{figures/dictionary3.pdf}
       \caption{}
        \label{fig:specW}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.47\linewidth}
        \centering
       \includegraphics[height=4.5cm]{figures/dictionary4.pdf}
        \caption{}
        \label{fig:ElementW}
    \end{subfigure}
    \caption{Example of the dictionary building with a 3 second extract of a car passage. In dashed lines, a 1 second $w_t$ window  (\subref{fig:specW}). With $w_t$ = 1 second, 3 spectra are then generated and included in $\mathbf{W}$ while for $w_t$ = $all$, the audio file is reduced into 1 spectral vector (\subref{fig:ElementW})}
    \label{fig:spec_elementW}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/bloc_diagram_NMF_EN.pdf}
    \caption{Specific block diagram of the NMF estimator with the dictionary design composed from a second sound database}
    \label{fig:bloc_nmf}
\end{figure}

@@

\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}C{2cm}@{}}
	\hline
    \textbf{\begin{tabular}[c]{@{}l@{}}experimental \\ factors\end{tabular}} & \textbf{modalities} & \begin{tabular}[c]{@{}C{2cm}@{}}\textbf{number}\\ \textbf{of modality}\end{tabular}\\ \toprule
\end{tabularx}

@@

\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}@{}C{2cm}}
	\hline
    \textbf{\begin{tabular}[c]{@{}l@{}}experimental \\ factors\end{tabular}} & \textbf{modalities} &\begin{tabular}[c]{@{}C{2cm}@{}}\textbf{number}\\ \textbf{of modality}\end{tabular}\\ \toprule
\end{tabularx}

@@

\begin{figure}[t!]
    \centering
    \begin{subfigure}[t]{0.47\linewidth}
        \centering
       \includegraphics[height=4.5cm]{figures/dictionary3.pdf}
       \caption{}
        \label{fig:specW}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.47\linewidth}
        \centering
       \includegraphics[height=4.5cm]{figures/dictionary4.pdf}
        \caption{}
        \label{fig:ElementW}
    \end{subfigure}
    \caption{Example of the dictionary building with a 3 second extract of a car passage. In dashed lines, a 1 second $w_t$ window  (\subref{fig:specW}). With $w_t$ = 1 second, 3 spectra are then generated and included in $\mathbf{W}$, while for $w_t$ = $all$, the audio file is reduced into 1 spectral vector (\subref{fig:ElementW})}
    \label{fig:spec_elementW}
\end{figure}
